An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/arch.tex
config: arch

Different from previous efforts, \eg, EnCore~\cite{zhang14encore},
which requires users or developers to provide explicit templates,
\app's learner encodes some predefined error-patterns 
to generate rules. 
As an illustration of a simple rule that we can learn,
consider an encoded pattern $X_1 \le X_2$, where $X_1$ and $X_2$ are
integer variables. The learner may derive the rule stating that
$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$. 
There is a classification and taxonomy of configuration errors in the 
existing work on automated configuration troubleshooting%
~\cite{yin11anempirical, configdataset}. 
Each class can be viewed as an error-pattern 
that \app should handle: we consider integer constraints, 
ordering errors, typing errors, correlation errors, etc.

@@

\para{Checking.}
The checker is used to detect rule violations in the configuration
files of interest. The inputs of the checker are the learned rules 
and the target configuration file to verify.
It generates a report (as shown in $\S$\ref{sec-motiv}) about 
whether it finds any error, \eg, rule violations 
or some suspicious values (\eg, singular value anomaly).
As shown in Figure~\ref{fig-overview},
there are two sub-modules in the checker. They are responsible for
checking rule violations and suspicious values, respectively.
In our experience, we find learned rules could be significantly reused
to check different configuration files, thus improving our usability.

>>>>

\com{Different from previous efforts, \eg, EnCore~\cite{zhang14encore},
which requires users or developers to provide explicit templates,
\app's learner encodes some predefined error-patterns 
to generate rules. 
As an illustration of a simple rule that we can learn,
consider an encoded pattern $X_1 \le X_2$, where $X_1$ and $X_2$ are
integer variables. The learner may derive the rule stating that
$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$. 
There is a classification and taxonomy of configuration errors in the 
existing work on automated configuration troubleshooting%
~\cite{yin11anempirical, configdataset}. 
Each class can be viewed as an error-pattern 
that \app should handle: we consider integer constraints, 
ordering errors, typing errors, correlation errors, etc.}

@@

\para{Checking.}
The checker is used to detect rule violations in the configuration
files of interest. The inputs of the checker are the learned rules 
and the target configuration file to verify.
It generates a report (as shown in $\S$\ref{sec-motiv}) about 
whether it finds any error, \eg, rule violations 
or some suspicious values (\eg, singular value anomaly).
As shown in Figure~\ref{fig-overview},
there are two sub-modules in the checker. They are responsible for
checking rule violations and suspicious values, respectively.
In our experience, we found learned rules could be significantly reused
to check different configuration files, thus improving our usability.
